---
title: "Current Data"
output:
  html_document:
    toc: no
    highlight: tango
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dpi = 300)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)


source(here::here('R', '00_vis_custom.R'))
source(here::here('R', '00_load-packages.R'))
```

```{r load-data, include = FALSE, results = FALSE}

source(here::here('R', '02.2_load_all_data.R')) # updated 2021-12-03
source(here::here('R', '04.1_all-figures.R'))

```

Contains all data from both ISCO and tank collection methods from all reserves that submitted data.

# TAL Sensor CHLA (RFU) vs. Extracted CHLA ($\mu$g/L) {.tabset .tabset-pills}

## All 

```{r}
all_figure
```

## Reserve and Methods

Current Data with reserves and the methods pulled out.

```{r}
all_reserve_method_figure
```

## Reserve and Methods (Interactive)

**How to use the interactive plot:** Hover over interactive plot for the tools panel to appear in top-right corner. Tools include: save plot, zoom, select (lasso or box), and data compare. Hover your cursor over a point for more information. You can also double click on an item in the legend to isolate that data series in the plot!

```{r, dpi = 120}
m = list(
    l = 80,
    r = 150,
    b = 80,
    t = 50,
    pad = 0
  )

all_interactive <- ggplotly(
                      all %>% 
                        ggplot(aes(x = chlorophyll_rfu, y = chla_ugl)) +
                        geom_point(aes(color = reserve_code, shape = method), position = "jitter") +
                        stat_smooth(method = "lm", color = "black", se = FALSE) +
                        scale_colour_manual(name = "Reserve", values = reservecolours) +
                        scale_shape_discrete(name = "Method") +
                        scale_y_continuous(expand = c(0,0)) +
                        theme_classic() +
                        labs(x = "Chlorophyll a (RFU) EXO",
                             y = "Chlorophyll a (ug/L) Extracted",
                             caption = "ISCO and tank experiments"),
                      tooltip = c("method", "chlorophyll_rfu", "chla_ugl", "reserve_code")
                      )
all_interactive %>% layout(margin = m)

rm(all_interactive, m)
```

## Tank vs ISCO

```{r}
tank_isco
```

{-}

***

# Summary Information

```{r tables-load, include = FALSE}
source(here::here('R', '06.1_tables-all.R'))
```

```{r summary-table, caption = ""}

sum_table_final  %>% 
  dplyr::select(-`temp*`, -`do_mgl*`) %>% # don't know where these columns come from (2021-08-13)
  kbl(align = "c", caption = 'Summary information for all parameters (Min-Max (Mean \U00B1 Standard Dev)) from each participating reserve for both tank and ISCO experiments. This table contains data that has not had QAQC flagged data removed. The temperature and dissolved oxygen data only contains data collected from the <i>in vivo</i> experiments with the ISCO.') %>% 
  kable_styling(fixed_thead = T) %>% 
  row_spec(0, bold = T) %>% 
  column_spec(1, border_right = T) %>% 
  column_spec(3, border_right = T) %>% 
  kable_classic(c('striped', 'hover'), html_font = "Open Sans", full_width = F)
```

***

# Interference Parameters {.tabset .tabset-pills}

These are the three parameters of interest in the interference testing studies. The following is the chlorophyll a fluorescence (RFU) from the EXO total algae sensor by the extracted $\mu$g/L with the three parameters of interest overlayed as color.

**How to use the interactive plot:** Hover over interactive plot for the tools panel to appear in top-right corner. Tools include: save plot, zoom, select (lasso or box), and data compare. Hover your cursor over a point for more information.

## fDOM 

```{r fdom-interf-interact, dpi = 120}

interference_interact_all_fxn(param = fdom, interact = TRUE)
# interference_interact_all_fxn(param = fdom, interact = FALSE) # to make it a still

```


## Turbidity

Had to filter to remove turbidity values > 240 NTU due to an outlier.

```{r turb-interf-interact, dpi = 120}

interference_interact_all_fxn(param = turbidity, interact = TRUE)
# interference_interact_all_fxn(param = turbidity, interact = FALSE) # to make it a still
```



## Temperature 

```{r temp-interf-interact, dpi = 120}

interference_interact_all_fxn(param = temperature, interact = TRUE)
# interference_interact_all_fxn(param = temperature, interact = FALSE) # to make it a still
```

