---
title: "Mission-Aransas"
output:
  html_document:
    toc: no
    highlight: tango
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dpi = 300)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)


source(here::here('R', '00_vis_custom.R'))
source(here::here('R', '00_load-packages.R'))
```

```{r load-data, include = FALSE, results = FALSE}

source(here::here('R', '02_load_data.R'))
source(here::here('R', '03_wrangle_data.R'))
source(here::here('R', '05_reserve-specific.R'))
source(here::here('R', '06_tables.R'))
```

# All Data {.tabset .tabset-pills}

## All

```{r all-data}
reserve_all_fxn("MAR") + 
  ggpubr::stat_regline_equation(label.y = 40) +
  ggpubr::stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`, `~")),
                   label.y = 38)
```

## Facet by Methods

```{r all-facet}
reserve_all_facet_fxn("MAR") + 
  ggpubr::stat_regline_equation(label.y = 40) +
  ggpubr::stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`, `~")),
                   label.y = 38)
```


{-}

# Interactive Plots for QAQC {.tabset .tabset-pills}

**How to use the interactive plot:** Hover over interactive plot for the tools panel to appear in top-right corner. Tools include: save plot, zoom, select (lasso or box), and data compare. Hover your cursor over a point for more information. You can also double click on an item in the legend to isolate that data series in the plot!

## ISCO Deployments

```{r isco, dpi = 120}
interact_reserve_isco_fxn("MAR")
```

## Tank Samples

```{r tank, dpi = 120}
interact_reserve_tank_fxn("MAR")
```



# Summary Tables {.tabset .tabset-pills}

## All Data

```{r table_all}
a <- reserve_sum_table_all('MAR')
  
a  %>% 
  kbl(align = "c", caption = 'All Data from ISCO and Tank Experiments. `chla_ugl` and `chla_rfu` are from extracted chlorophyll a samples') %>% 
  kable_styling(fixed_thead = T) %>% 
  row_spec(0, bold = T) %>% 
  column_spec(1, border_right = T) %>% 
  kable_classic(c('striped', 'hover'), html_font = "Open Sans", full_width = F)
```

## ISCO Data Only

```{r table_isco}
b <- reserve_sum_table_isco('MAR')
  
b  %>% 
  kbl(align = "c", caption = 'Only data from ISCO Experiments. `chla_ugl` and `chla_rfu` are from extracted chlorophyll a samples') %>% 
  kable_styling(fixed_thead = T) %>% 
  row_spec(0, bold = T) %>% 
  column_spec(1, border_right = T) %>% 
  kable_classic(c('striped', 'hover'), html_font = "Open Sans", full_width = F)
```

## Tank Data Only

```{r table_tank}
c <- reserve_sum_table_tank('MAR')
  
c  %>% 
  kbl(align = "c", caption = 'Only data from Tank Experiments. `chla_ugl` and `chla_rfu` are from extracted chlorophyll a samples') %>% 
  kable_styling(fixed_thead = T) %>% 
  row_spec(0, bold = T) %>% 
  column_spec(1, border_right = T) %>% 
  kable_classic(c('striped', 'hover'), html_font = "Open Sans", full_width = F)
```

# Interactive Interference Parameters {.tabset .tabset-pills}

These are the three parameters of interest in the interference testing studies. The following is the chlorophyll a fluorescence (RFU) from the EXO total algae sensor by the extracted $\mu$g/L with the three parameters of interest overlayed as color for the specific reserve of interest.

**How to use the interactive plot:** Hover over interactive plot for the tools panel to appear in top-right corner. Tools include: save plot, zoom, select (lasso or box), and data compare. Hover your cursor over a point for more information. You can also double click on an item in the legend to isolate that data series in the plot!

## fDOM

```{r fdom-interf, dpi = 120}
interact_reserve_interf_fxn("MAR", param = fdom)
```

## Turbidity

```{r turb-interf, dpi = 120}
interact_reserve_interf_fxn("MAR", param = turbidity)
```

## Temperature

```{r temp-interf, dpi = 120}
interact_reserve_interf_fxn("MAR", param = temperature)
```
