---
title: "Tank Data <div><i> in situ </i></div>"
output:
  html_document:
    toc: no
    highlight: tango
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dpi = 300)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)


source(here::here('R', '00_vis_custom.R'))
source(here::here('R', '00_load-packages.R'))
```

```{r load-data, include = FALSE, results = FALSE}

source(here::here('R', '02_load_data.R'))
source(here::here('R', '03_wrangle_data.R'))

```

Contains all data from the tank (*in situ*) collection method from all reserves that submitted data.

# TAL Sensor CHLA (RFU) vs. Extracted CHLA ($\mu$g/L) {.tabset .tabset-pills}

## All 

```{r}
source(here::here('R', '04.3_tank-figures.R'))

all_tank_figure
```

## Reserve Single

```{r}
all_tank_reserve_figure
```

## All Reserves (w/stats)

```{r}
facet_all_tank_figure_stat
```

## All Reserves (no stats)

```{r}
facet_all_tank_figure
```

{-}

# Interference Parameters {.tabset .tabset-pills}

These are the three parameters of interest in the interference testing studies. The following is the chlorophyll a fluorescence (RFU) from the EXO total algae sensor by the extracted $\mu$g/L with the three parameters of interest overlayed as color.


## fDOM 

```{r isco-fdom-interf}
all_tank_fDOM
```

## Turbidity 

Had to filter to remove turbidity values > 240 NTU due to an outlier.

```{r isco-turb-interf}
all_tank_turb
```

## Temperature 

```{r temp-interf}
all_tank_temp
```

{-}
