---
title: "NERRS Chlorophyll Catalyst Project"
subtitle: 'Data Update Version 2.0'
date: 'Created 2021-06-25 (updated: `r Sys.Date()`)'
output:
  html_document:
    toc: yes
    toc_float: 
      collapsed: false
    toc_depth: 2
    highlight: tango
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dpi = 300)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)


source(here::here('R', '00_vis_custom.R'))
source(here::here('R', '00_load-packages.R'))
```

```{r load-data, include = FALSE, results = FALSE}

source(here::here('R', '02_load_data.R'))
source(here::here('R', '03_wrangle_data.R'))

```


# Current Data

Data was last downloaded for inclusion in update on 2021-08-03.

Reserves with submissions this round:
```{r reserves-1}
reserves <- tribble(
  ~no, ~reserve,
  1, "ELK",
  2, "GND",
  3, "GRB",
  4, "GTM",
  5, "HEE", 
  6, "LKS", 
  7, "MAR",
  8, "NIW",
  9, "OWC", 
  10, "PDB", 
  11, "SAP", 
  12, "WEL", 
  13, "WKB" 
)

a <- as_tibble(unique(all$reserve_code)) %>% rename(reserve = value) %>% mutate(Submission = "X")
b <- as_tibble(unique(isco$reserve_code)) %>% rename(reserve = value) %>% mutate(ISCO = 'X')
c <- as_tibble(unique(tank$reserve_code)) %>% rename(reserve = value) %>% mutate(Tank = 'X')

d <- left_join(reserves, a, by = "reserve") %>% 
        left_join(b, by = "reserve") %>% 
        left_join(c, by = "reserve") %>% 
        select(-no) %>% 
        rename(Reserve = reserve)

d <- sapply(d, as.character)
d[is.na(d)] <- " "
d <- as.data.frame(d)

d %>% 
  kbl(align = "c") %>% 
  kable_styling(fixed_thead = T) %>% 
  row_spec(0, bold = T) %>% 
  column_spec(1, border_right = T) %>% 
  kable_classic(c('striped', 'hover'), html_font = "Open Sans", full_width = F)

rm(reserves, a, b, c, d)
```

<br>

<right><blockquote class="blockquote text-right">
  <p class="mb-0">The greatest value of a picture is when it forces us to notice what we never expected to see.</p>
  <footer class="blockquote-footer">John W. Tukey</footer>
</blockquote></right>

<br> 

## All Data {.tabset .tabset-pills}

Contains all data from both ISCO and tank collection methods from all reserves that submitted data.

### All 

```{r}
source(here::here('R', '04.1_all-figures.R'))

all_figure
```

### Reserve and Methods

Current Data with reserves and the methods pulled out.

```{r}
all_reserve_method_figure
```

### Reserve and Methods (Interactive)

```{r, dpi = 120}
ggplotly(
  all %>% 
    dplyr::filter(qaqc == 0) %>% 
    ggplot(aes(x = chlorophyll_rfu, y = chla_ugl)) +
    geom_point(aes(color = reserve_code, shape = method), position = "jitter") +
    stat_smooth(method = "lm", color = "black", se = FALSE) +
    scale_colour_manual(name = "Reserve", values = reservecolours) +
    scale_shape_discrete(name = "Method") +
    scale_y_continuous(expand = c(0,0)) +
    theme_classic() +
    labs(x = "Chlorophyll a (RFU) EXO",
         y = "Chlorophyll a (ug/L) Extracted",
         caption = "ISCO and tank experiments"),
  tooltip = c("method", "chlorophyll_rfu", "chla_ugl", "reserve_code")
  )
```

### Tank vs ISCO

```{r}
tank_isco
```

# {-}


## Interference Parameters {.tabset .tabset-pills}

Had to filter to remove turbidity values > 240 NTU due to an outlier.

### Still

```{r all-interf}

fdom

turb

temp

```

### Interactive

```{r all-interf-interact, dpi = 120}

ggplotly(all %>%
           filter(chlorophyll_rfu > 0) %>%
           ggplot(aes(x = chlorophyll_rfu, y = chla_ugl, group = reserve_code)) +
           geom_point(aes(color = fdom_qsu), size = 3) +
           scale_color_continuous(name = "fDOM QSU") +
           ggpubr::theme_classic2() +
           labs(x = 'Chlorophyll a RFU EXO',
                y = 'Chlorophyll a ug/L Extracted',
                title = "fDOM",
                caption = "Both Tank and ISCO Experiments"),
         tooltip = c("fdom_qsu", "chlorophyll_rfu", "chla_ugl", "reserve_code"))


ggplotly(all %>%
           filter(chlorophyll_rfu > 0 & turb < 240) %>%
           ggplot(aes(x = chlorophyll_rfu, y = chla_ugl, group = reserve_code)) +
           geom_point(aes(color = turb), size = 3) +
           scale_color_continuous(name = "Turbidity NTU")  +
           ggpubr::theme_classic2() +
           labs(x = 'Chlorophyll a RFU EXO',
                y = 'Chlorophyll a ug/L Extracted',
                title = "Turbidity", caption = "Both Tank and ISCO Experiments"),
         tooltip = c("turb", "chlorophyll_rfu", "chla_ugl", "reserve_code"))

ggplotly(all %>%
           filter(chlorophyll_rfu > 0) %>%
           ggplot(aes(x = chlorophyll_rfu, y = chla_ugl)) +
           geom_point(aes(color = temp), size = 3) +
           scale_color_gradient(name = 'Temperature C',
                                low="blue", high="red") +
           scale_color_continuous(name = expression(paste('Temperature ', "(", degree, "C)"))) +
           ggpubr::theme_classic2() +
           labs(x = 'Chlorophyll a RFU EXO',
                y = 'Chlorophyll a ug/L Extracted',
                title = "Temperature", caption = "Both Tank and ISCO Experiments"),
         tooltip = c("temp", "chlorophyll_rfu", "chla_ugl", "reserve_code"))

```

# {-}

## ISCO Only {.tabset .tabset-pills}

Contains only data submitted as part of ISCO collections.

### All 

```{r}
source(here::here('R', '04.2_isco-figures.R'))

all_isco_figure
```

### Reserve Single

```{r}
all_isco_reserve_figure
```

### All Reserves (w/stats)

```{r}
facet_all_isco_figure_stat
```

### All Reserves (no stats)

```{r}
facet_all_isco_figure
```

### Interference

Had to filter to remove turbidity values > 240 NTU due to an outlier.

```{r}
all_isco_fDOM

all_isco_turb

all_isco_temp
```

# {-} 

## Tank Only {.tabset .tabset-pills}

Contains only data submitted as part of ISCO collections.

### All 

```{r}
source(here::here('R', '04.3_tank-figures.R'))

all_tank_figure
```

### Reserve Single

```{r}
all_tank_reserve_figure
```

### All Reserves (w/stats)

```{r}
facet_all_tank_figure_stat
```

### All Reserves (no stats)

```{r}
facet_all_tank_figure
```

### Interference

```{r}
all_tank_fDOM

all_tank_turb

all_tank_temp
```

# {-}

# Interference Testing {.tabset .tabset-pills}

## Temperature

Equation 1 (Watras et al. 2017): 
$F_{r} = \frac{F_{m}}{1 + \rho(T_{m} - T_{r})}$

Currently, only data from GTMNERR:

```{r, results = FALSE, include = FALSE}
source(here::here('R', 'interference', '01_temp-load-wrangle-run.R'))

```

```{r, fig.cap = "Temperature quenching of chlorophyll (A) fluorescence in unfiltered water from Pellicer Creek, Florida. The temperature quench was removed (B) by adjusting the raw data to a reference temperature of 20 ('~*degree*C') using Eq. 1."}

(plot.a + labs(x = '', title = 'A')) / (plot.d + labs(title = 'B')) 

```

General comments:

+   Slight jump in non-diluted water
+   Non-linear at higher temps
+   Slopes at different concentrations don’t follow Watras pattern
+   Slope in blank - could indicate sensor problem rather than, or in addition to, quenching
+   Applying Watras equation correction didn’t seem to work
+   Re-run experiment?
+   May need to use mixed effects model (Watras equation 4) to account for the effects of temperature on both the sensor and the energy decay pathways 


## Turbidity

Currently, only data from North Inlet-Winyah Bay:

```{r, results = FALSE, include = FALSE}
source(here::here('R', 'interference', '02_turb-load-wrangle-run.R'))
```

```{r, fig.cap = "Average turbidity (FNU) and chlorophyll fluorescence (RFU) from three separate trials"}
turb_interf
```

## fDOM

Currently, only data from North Inlet-Winyah Bay:

```{r}
source(here::here('R', 'interference', '03_fdom-load-wrangle-run.R'))
```

```{r, fig.cap ="Average fluorescent dissolved organic matter (QSU) and chlorophyll fluorescence (RFU) from one trial"}
fdom_interf
```

General comments:

+   Didn’t get up to max QSU seen in system (~120)
+   Compared to natural data, when QSU is high, RFU are not as high as they got in experiment

# {-}


# Algae Species

From Mission-Aransas

```{r, results = FALSE, include = FALSE}
source(here::here('R', '10_algae-species.R'))
```

```{r, fig.cap = "Different species of algae used in tank experiments in Mission-Aransas NERR.", dpi = 120}

ggplotly(dat2 %>%  
          ggplot(aes(x = mean_rfu, y = mean_ugl)) +
          geom_point(aes(color = algae), size = 3) +
           scale_color_discrete(name = "Algae") +
           theme_classic() +
           labs(x = "Chlorophyll a (RFU) EXO",
                y = "Chlorophyll a (ug/L) Extracted"),
         tooltip = c("algae", "mean_rfu", "mean_ugl")
         )

```

# Session Info

```{r, results = T}
sessionInfo()
```